Model 

### 2019-10-03 04_estimation.Rmd
Corrrect spatial chi-squared test statistic

  tibble(
    Hstat = t(db) %*% MASS::ginv(dV) %*% db, 
    "p-value" = pchisq(Hstat, df = Matrix::rankMatrix(dV))
  )
}
slx_hausman(access_slx_wc, access_sdem_wc)
slx_hausman(access_slx_wd, access_sdem_wd)
```

>>>>

  tibble(
    Hstat = t(db) %*% MASS::ginv(dV) %*% db, 
    "p-value" = pchisq(Hstat, df = Matrix::rankMatrix(dV), lower.tail = FALSE)
  )
}
slx_hausman(access_slx_wc, access_sdem_wc)
slx_hausman(access_slx_wd, access_sdem_wd)
```
